Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to get GLAD/EDGI prepan positive diagnosis for mdd

@@

###Retro
####Style 1

@@

####Style 2

>>>>

```
###Prepan

```{r Get anxiety positive for GLAD/EDGI}

GLAD.prepan_mdd_positive <- GLAD.prepan %>%
  group_by(Sample) %>% 
  select(depressive_disorders_numeric) %>% 
  filter(depressive_disorders_numeric == 1)

GLAD.prepan_mdd_positive <- GLAD.prepan_mdd_positive %>% 
  group_by(Sample) %>% 
  summarise("Depressive disorders" = n())

@@

#### Plot Style 1

@@

####Plot Style 2
